---
title: "SentimentIt"
author: ""
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sentimentIt_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a tutorial on how to use the SentimentIt R package. SentimentIt provides a pairwise comparison framework for fast, flexible, and reliable human coding of political texts.

###Probably want to include some background on SentimentIt here###

1. Before interacting with the package in R, go to the following link: https://www.sentimentit.com/documentation/getting_started. The manual attached to the link explains how to create the necessary accounts with Amazon and SentimentIt so you can interact with Mechanical Turk. A SentimentIt account MUST be created before the R functionality can be used. 

2. Once the five steps of the SentimentIt manual are completed, install the SentimentIt package in R using the following command:

```{r, eval = FALSE}
install.packages("SentimentIt")

#or if the package is already installed

library("SentimentIt")
```

3. Once the package is installed, identify yourself to the SentimentIt API from R using the `authenticate()` function. Input as character vectors the email and password used to create your SentimentIt account.

```{r, eval = FALSE}
authenticate(email = "johndoe@school.edu", password = "12345")
```

After running this function, the R console will return a character vector containing the authentication token for your session.

4. 
